A Survey of Possible Exoskeleton Control Architectures and Algorithms\\ (Draft 2.3)

### 2015-09-24 control.tex
cga-fixes

Low level control presents an API (Application Programmer Interface)
for higher control levels
to access the actuators, sensors, and other robot hardware.
It implements high servo rate processing including feedback control and online
optimization.
This level provides an idealization of the exoskeleton in two ways: 
What degrees of freedom (DOF) are controlled, and how is a degree of
freedom controlled?

@@

>>>>

Low level control presents an API (Application Programmer Interface)
for higher control levels
to access the actuators, sensors, and other robot hardware~\cite{IEEE07271219}.
It implements high servo rate processing including feedback control and online
optimization.
This level provides an idealization of the exoskeleton in two ways: 
What degrees of freedom (DOF) are controlled, and how is a degree of
freedom controlled?

@@

Another approach to shared control is allocating time slices or providing assistance
on an as-needed basis~\cite{IEEE07140030}.
